\chapter{Auxiliary Results}
\label{A:auxiliary-app}

The $c_r$-inequality and following corollary will provide useful
bounds to come.
\begin{theorem}[The $c_r$-inequality]
  \label{T:c_r-inequality}
  Let $X$ and $Y$ be random variables and $r > 0$.  Suppose that
  $\E|X|^r < \infty$ and $\E|Y|^r < \infty$.  Then
  \begin{equation}
    \E|X + Y|^r < c_r(\E|X|^r+\E|Y|^r),
  \end{equation}
  where $c_r = 1$ when $r \leq 1$ and $c_r = 2^{r-1}$ when $r \geq 1$.
\end{theorem}

\begin{corollary}
  \label{C:sum_variance}
  Suppose that $\var(X) < \infty$ and $\var(Y) < \infty$.  Then
  \begin{equation}
    \var(X + Y) < 2(\var(X)+\var(Y)).
  \end{equation}
\end{corollary}
\begin{proof}
  This follows immediately by applying Theorem~\ref{T:c_r-inequality}
  to the centered random variables $X' = X - \E X$ and $Y' = Y -
  \E Y$.
\end{proof}

\begin{lemma}
  \label{L:antisymmetric}
  If $(W, W')$ is an exchangeable pair, then $\E g(W, W') = 0$ for all antisymmetric
  measurable functions such that the expected value exists.
\end{lemma}

Here is a slight generalization of Lemma 2.7 from \cite{chen2010normal}:
\begin{lemma}
  Let $(W, W')$ be an approximate Stein pair and $\Delta = W - W'$.  Then
  \begin{equation}
    \E W = \E R \quad \text{ and } \quad \E \Delta^2 = 2 \lambda \E W^2 - 2\lambda \E WR
    \quad \text{ if } \E W^2 < \infty.
  \end{equation}
  Furthermore, when $\E W^2 < \infty$, for every absolutely continuous function $f$ satisfying
  $|f(w)| \leq C(1 + |w|)$, we have
  \begin{equation}
    \label{eq:expectation-w-f(w)}
    \E Wf(W) = \frac{1}{2\lambda} \E (W-W')(f(W)-f(W')) + \E f(W)R.
  \end{equation}
\end{lemma}
\begin{proof}
  From (\ref{D:approx-stein-pair}) we have
  \begin{equation*}
    \E [\E [W-W'|W]] = \E \lambda (W - R) = \lambda \E W - \lambda \E R.
  \end{equation*}
  We also have
  \begin{equation*}
    \E [\E [W-W'|W]] = \E W - \E [\E [W' | W]] = \E W - \E W' = 0
  \end{equation*}
  using exchangeability.  Equating the two expressions yields
  \begin{equation*}
    \E W = \E R
  \end{equation*}

  As an intermediate computation,
  \begin{equation}
    \label{E:EW'W}
    \begin{split}
      \E W'W &= \E [\E [W'W|W]] \\
      &= \E [W \E [W'|W]] \\
      &= \E [W ((1-\lambda)W+\lambda R)] \quad \text{ from } \eqref{D:approx-stein-pair} \\
      &= (1-\lambda)\E W^2 + \lambda \E WR.
    \end{split}
  \end{equation}
  Then
  \begin{equation}
    \begin{split}
      \E \Delta^2 &= \E (W-W')^2 \\
      &= \E W^2 + \E W'^2 - 2\E W'W \\
      &= 2 \E W^2 - 2 ((1-\lambda)\E W^2 + \lambda \E WR) \quad \text{ from } \eqref{E:EW'W}\\
      &= 2 \lambda \E W^2 - 2\lambda \E WR.
    \end{split}
  \end{equation}

  By the linear growth assumption on $f$, $\E g(W, W')$ exists for the antisymmetric function
  $g(x,y) = (x-y)(f(y)+f(x))$.  By Lemma~\ref{L:antisymmetric},
  \begin{equation*}
    \begin{split}
      0 &= \E (W-W')(f(W')+f(W)) \\
      &= \E (W-W')(f(W')-f(W)) + 2\E f(W)(W-W') \\
      &= \E (W-W')(f(W')-f(W)) + 2\E [f(W)\E [(W-W')|W]] \\
      &= \E (W-W')(f(W')-f(W)) + 2\E f(W)(\lambda (W-R)).
    \end{split}
  \end{equation*}
  Rearranging the expression yields
  \begin{equation}
    \E Wf(W) = \frac{1}{2\lambda} \E (W-W')(f(W)-f(W')) + \E f(W)R.
  \end{equation}
\end{proof}

This is just a small part of Lemma 2.4 from \cite{chen2010normal}:
\begin{lemma}
  \label{L:stein-eq-sol-bound}
  For a given function $h: \mathbb{R} \to \mathbb{R}$, let $f_h$ be the solution to the Stein
  equation.  If $h$ is absolutely continuous, then
  \begin{equation}
    ||f_h|| \leq 2 ||h'||.
  \end{equation}
\end{lemma}

Lemma 2.2 from \cite{chen2010normal}:
\begin{lemma}
  \label{L:stein-eq-sol}
  For fixed $z \in \mathbb{R}$ and $\Phi(z) = P(Z \leq z)$, the unique bounded solution
$f_z(w)$ of the equation
  \begin{equation}
    \label{eq:stein-eq}
    f'(w) - wf(w) = \mathbf{1}_{\{w \leq z\}} - \Phi(z)
  \end{equation}
  is given by
  \begin{equation}
    \label{eq:fz}
    f_z(w) =
    \begin{cases}
      \sqrt{2 \pi} e^{w^2/2} \Phi(w)[1-\Phi(z)] \quad \text{if } w \leq z \\
      \sqrt{2 \pi} e^{w^2/2} \Phi(z)[1-\Phi(w)] \quad \text{if } w > z. \\
    \end{cases}
  \end{equation}
\end{lemma}

Part of Lemma 2.3 from \cite{chen2010normal}:
\begin{lemma}
  \label{L:stein-eq-sol-bound2}
  Let $z \in \mathbb{R}$ and let $f_z$ as in (\ref{eq:fz})
    Then
    \begin{equation*}
      |(w + u)f_z(w + u) - (w + v)f_z(w + v)| \leq
      (|w| + \sqrt{2 \pi} / 4)(|u| + |v|).
    \end{equation*}
\end{lemma}
